The pollination trade-off

### 2018-07-27 paper/manuscript.Rmd
Specify hetero and conspecific pollen in the intro

Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool lmight be involved.
For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 
This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly. 
If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators. 
In this case, a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.

Here, we explore the signature of the mutualistic trade-off in diverse natural communities. 
To tease appart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that ocurr within it, all while accounting for the traits of the species that integrate the community.
Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
Second, we investigate wether there is a relationship between this gain and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context. 
Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
**TODO: Mini conclusion here**

@@

We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.

>>>>

Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool might be involved.
For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 
This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly. 
If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators. 
In this case, a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.

Here, we explore the signature of the mutualistic trade-off in diverse natural communities. 
To tease appart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that ocurr within it, all while accounting for the traits of the species that integrate the community.
Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
Second, we investigate wether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context. 
Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators. 
We hypothezise that XX??
**TODO: Mini conclusion here**

@@

Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas. 
We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.
